GEE models

### 2017-10-15 doc/esm.Rmd
more detail on QIC

QIC is a technique that balances the goodness of fit of the model with its
relative complexity (i.e. number of covariates) against other models being
compared. This identifies a specific model from a number of models that is the
'best' fit and least complex of all the models. QIC and other information
criterion methods are used in conjunction with other techniques such as
literature and DAG based. The final GEE model selected as best fitting was
negligibly different when using insulin sensitivity or beta-cell function as an
outcome and as such the same covariates were chosen for models with each of the
outcomes. The covariates medication use, WC, ALT, and MET would be considered
classical confounders while TAG would be considered a mediating variable.

>>>>

QIC is a technique that balances the goodness of fit of the model with its
relative complexity (i.e. number of covariates) against other models being
compared. QIC, more so then the more common AIC, penalizes the inclusion of more
variables in the model. This technique is used to compare multiple models to
identify the model with the highest fit and with the lowest complexity (variables),
*of the models compared*. QIC is similar to AIC, except AIC is based on maximum
likelihood of models such as mixed effects models. Since GEE does not use
maximum likelihood, AIC can not be used. QIC and other information
criterion methods are used in conjunction with other techniques such as
literature and DAG based. The final GEE model selected as best fitting was
negligibly different when using insulin sensitivity or beta-cell function as an
outcome and as such the same covariates were chosen for models with each of the
outcomes. The covariates medication use, WC, ALT, and MET would be considered
classical confounders while TAG would be considered a mediating variable.
